---
title: "Nonlinear Relationships Parenchyma"
author: "Paul Klemm, Mehdi Arian Alborzi and Bernhard Preim"
date: "19. Januar 2016"
output: html_document
---

This R Markdown document aims to identify nonlinear relationships of a breast cancer data set from the [Study of Health in Pomerania](https://www.medizin.uni-greifswald.de/cm/fv/ship.html).

At first, load the data and give an overview over the target feature, which is the percentage of the parenchyma tissue in the female breast.

```{r}
# Load the data
path_to_data <- '/Users/paul/Workshop/Promotion/Data/Breast Fat Dataset/breast_fat_imageonly_labels.csv'
raw_data <- read.csv(path_to_data)
# The target variable is `Segmentation_ParenchymToVolume
summary(raw_data$Segmentation_ParenchymToVolume)
# Filter numeric variables (https://stackoverflow.com/questions/5863097/selecting-only-numeric-columns-from-a-data-frame)
numerical_data <- raw_data[ , sapply(raw_data, is.numeric)]
```

We want to extract nonlinear relationships of all numerical variables with the parenchyma tissue share. This is carried out by applying a polynomial regression models. The notation on how to conduct a polynomial regression is taken from [this blog post](http://www.r-bloggers.com/polynomial-regression-techniques/). The basic notation is `numerical_data$Segmentation_ParenchymToVolume ~ numerical_data$numeric_var + I(numerical_data$numeric_var^2)`.

```{r}
# Calculate linear models with all variables
polynomial_models = list()
for (dimension in names(numerical_data)) {
  model_formula <- paste("numerical_data$Segmentation_ParenchymToVolume ~ numerical_data$", dimension, "+ I(numerical_data$", dimension, "^2)", sep="")
  polynomial_models[dimension] <- lm(formula = model_formula)
  print(model_formula)
}
```

Print all models.

```{r fig.width=5, fig.height=5}
#for (dimension in names(numerical_data)) {
#  # ToDo Continue here
#  plot(numerical_data[dimension], numerical_data$Segmentation_ParenchymToVolume)
#  points(numerical_data[dimension], predict(polynomial_models[[dimension]]), col="red")
}
```

# Tests

Here is the code to visualize the result of a linear model fitted to a scatterplot of the underlying data.

```{r, fig.width=5, fig.height=5}
polynomial_model <- lm(formula = numerical_data$Segmentation_ParenchymToVolume ~ numerical_data$Age + I(numerical_data$Age^2))
# Plot the result
plot(numerical_data$Age, numerical_data$Segmentation_ParenchymToVolume)
points(numerical_data$Age, predict(polynomial_model), col="red")
# https://stackoverflow.com/questions/28114677/calculate-curvature-from-smooth-spline-in-r
```
